---
title: "18_12_18_Rmarkdown"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "NexisUni_pdf_scraping"
author: "Delaney Roney"
date: "December 18, 2018"
output: Word Document
---

```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Outline of lexisUni text analysis (checked if done):
 1. Dowload pdf from lexisUni - search terms: "Master Project Name" AND "Project Developer" AND "wind" AND "energy' (if necessary, the state was added in the search term if location was not precise enough. 
 2. Save pdf in sample_pdfs folder x
      Each pdf saved as "fulltext"+ # search results if <10" + "abbreved project developer" "# of results pages in         >10", collapsed with "_" x
2. Create a df with everypdf in each row. my_data x
3. Create df with unested text unested,such that each row is a pdf page.x
4. Created new df that splits each page by word, sch that every row is a word in the text (unest_tokens where tokens are pdf) x
5. Get word count of specific words through group_by()
Conduct sentiment analysis on unique words x 
6. get hits and number of hits of different 'negative words' x
# Following meeting 10/22/18:
1. Unest token by group of words or sentences and conduct sentiment analysis on this.
2. Clean scripts - ID words in pdf that consistently pop up and need to be filtered out.
3. separate headlines from text to ensure we don't have duplicates
4. create csv format (NAME, Developer, State, Sentiment, subjectivity ...)
Other notes: 
*tidytext::tokenize function - every element in list become df. rbind dfs 
 str_count() how many times does a search term come up 
 str_match()
 regex() 
```{r packages_read_in}
### Packages 
# install.packages("pdftools", "devtools")
library(pdftools)
library(tm)
# library(tm.plugin.lexisnexis)
library(devtools)
# install.packages("tidytext")
library(tidytext)
library(broom)
# install.packages("tidyverse")
library(data.table)
library(tidyverse)
library(purrr)
library(googledrive)
library(knitr)
library(readr)
```


```{r connect_to_googledrive}
#drive_auth()
# the google drive folder id is simply the id in the folder url after the last dash
# so the id here is derived from https://drive.google.com/drive/folders/1kZuJF3eS7SIiC8VBeGc6vVNvpBZHLnxg?ogsrc=32
# Create folder in desktop for pdfs. Decided to set on desktop to be compatible with all computers.
#All_LexisUni_PDFs <- "H:/Desktop/All_LexisUni_PDFs"
#dir.create(All_LexisUni_PDFs, showWarnings = FALSE) 
  # if already created, won't edit it. 
## Access to top level NexisUni folder in gdrive
# GPteam_drive_id <- "1kZuJF3eS7SIiC8VBeGc6vVNvpBZHLnxg?ogsrc=32"
# #create a dribble of Nexis Uni articles 
# NexisUni_folder_gdrive <- googledrive::drive_ls(googledrive::as_id(GPteam_drive_id))
## Access to  WindBelt GP/NexisUni/All_LexisUni_PDF folder in gdrive
#All_LexisUni_PDFs_id  <- "1Jl5lnAMP8XccxzKEm2A4LwFgg_sNhPxN?ogsrc=32"
#All_LexisUni_PDFs_folder <- googledrive::drive_ls(googledrive::as_id(All_LexisUni_PDFs_id))
#View(All_LexisUni_PDFs_folder)
# function to download all lexisUni pdfs
#pdf_downloader <- function(templates_dribble, local_folder){
  # download all pdfs
 #     for (i in 1:nrow(templates_dribble)){
  #  drive_download(as_id(templates_dribble$id[[i]]), 
   #                file.path(local_folder, templates_dribble$name[[i]]),
#    #               overwrite = TRUE) #check if overwrite is neede here
#  }
#}
#pdf_downloader(sample_n(All_LexisUni_PDFs_folder,20), All_LexisUni_PDFs)


#Delaney Code for Bringing in csv and pdfs from google drive

#WindBelt_Data <- drive_download(as_id("https://docs.google.com/spreadsheets/d/1obj9RRgbt9XGudtZW-v_7QNiOuWrN3gdSb9RKmRBgco/edit#gid=146899731"), path = "ventyx_converted_11_27_2018_PopDensity_Income_Viewshed_lowhighimpact_doc_names", type = "csv", overwrite = TRUE)

#WindBelt_Full <- read.csv("~/Downloads/ventyx_converted_11_27_2018_PopDensity_Income_Viewshed_lowhighimpact_doc_names.csv")
#View(WindBelt_Full)

#############

#Download pdfs from team drive then loadin as file name Windbelt_pdfs

#Lexis Uni
#Desktop Comp
#ventyx_converted_01_08_2019_PopDensity_Income_Viewshed_lowhighimpact_doc_names_IncomeMedian <- read.csv("D:/Desktop/ventyx_converted_01_08_2019_PopDensity_Income_Viewshed_lowhighimpact_doc_names_IncomeMedian.csv")

#View(ventyx_converted_01_08_2019_PopDensity_Income_Viewshed_lowhighimpact_doc_names_IncomeMedian)


#mac Comp

ventyx_converted_01_08_2019_PopDensity_Income_Viewshed_lowhighimpact_doc_names_IncomeMedian <- read.csv("~/Desktop/ventyx_converted_01_08_2019_PopDensity_Income_Viewshed_lowhighimpact_doc_names_IncomeMedian.csv")

View(ventyx_converted_01_08_2019_PopDensity_Income_Viewshed_lowhighimpact_doc_names_IncomeMedian)

WindBelt_Full <- ventyx_converted_01_08_2019_PopDensity_Income_Viewshed_lowhighimpact_doc_names_IncomeMedian

Windbelt_Project_Database_H_L_W <- mutate(WindBelt_Full, H_L_W = ifelse(lr_tif>0, "Low", "High"))

wind_df <- Windbelt_Project_Database_H_L_W

#google news
google_news <- google_News_scrape <- read_csv("~/Desktop/google_scraping_01-08-19.csv")
View(google_news)





```


```{r directory_setup}


#LU
directory1 <- "D:/Desktop/All_LexisUni_PDFs"
directory1
# directory <- G:/TextAnalysis/NexisUni/Margaux_PDFs
# directory <- G:/TextAnalysis/NexisUni/
#change path if not on windbelt comp.

#Google News

#Desktop Computer
#directory1 <- "D:/Desktop/All_LexisUni_PDFs"
#directory1

#Mac Computer
directory1 <- "~/Desktop/All_LexisUni_PDFs"
directory1

pdfs <- paste(directory1, "/", list.files(directory1, pattern = "*.pdf", ignore.case = T), sep = "")

pdfs_names <- list.files(directory1, pattern = "*.pdf", ignore.case = T)
#pdfs_names

pdfs_text <- purrr::map(pdfs, pdftools::pdf_text)
#head(pdfs_text)
```
#### Dataframe 1 with just pdfs and full text of the pdf
```{r dataframe1}
#LU

#each row is a pdf doc name (document) with the full pdf text
#projects_pdftext <- data_frame(document = pdfs_names, text = pdfs_text)
#head(projects_pdftext)
#View(projects_pdftext)
# text column : each row is an element of a list 


#Googlenews

projects_pdftext <- data_frame(document = google_news$ProjectName, text = google_news$FullText)

#document = project name


```
#### Dataframe 2 spliting text by page
```{r dataframe2}
# dataset with each page in one row
project_pdfpages <- projects_pdftext %>% 
  unnest() # splits pdf text by page and removes list format ( c("")) since each element of the list is now its own row.
View(project_pdfpages)
```
#### Dataframe 3 spliting page text by word (unnest_tokens())
```{r dataframe3}
#Dataset with each work in or row associated with its pdf source 
projects_pdfwords <- projects_pdftext %>% 
  unnest() %>% 
  tidytext::unnest_tokens(output = word, input = text, token = 
                          "words", to_lower = T
                # strip_numeric = TRUE
                )%>%      
  filter(!word %in% c("lexis",
                      "nexis", "Uni",
                      "about lexisnexis",
                      "Privacy Policy",
                      "Terms & Conditions", "Copyright © 2018 LexisNexis",
                      " | ",  "@", "lexisnexis")) 
# %>% gsub("[^A-Za-z0-9,;._-]","")
#View(projects_pdfwords)

#If google news only run chunk after this
View(projects_pdftext)
projects_pdfwords <- projects_pdftext %>% 
  tidytext::unnest_tokens(output = word, input = text, token = "words", to_lower = T)


#projects_pdfnest <- projects_pdftext %>% 
#  unnest() %>% 
#  tidytext::unnest_tokens(output = ngrams, input = text, token = "ngrams", n = 5, to_lower = T)

# View(my_data4)

# note: unnest_tokens() splits text by respective element (ie word, phrase, ...) word is default

```




#### Dataframe wordsgrouped by pdf and summarised by frequency of word or ngrams
```{r group_by}
projects_pdfwords_count <- projects_pdfwords %>%
  group_by(document, word) %>% 
  summarise(count = n())
# View(projects_pdfwords_count)
# counts the number of time a specific words is found in the page pdf.
# View(my_data2_sum)
projects_pdfnest_count <- projects_pdfnest %>%
  group_by(document, ngrams) %>% 
  summarise(count = n())
# View(projects_pdfnest_count)
# add new count column with most freq. words
```

#### Sentiment dictionaries:

Compare sentiment dictionaries
```{r sentimentdictionaries}
# using 'afinn' vs. 'nrc sentiment tests.
get_sentiments("afinn") # associates word with a sentiment score
#afinn scores/ranks from -5 to +5 for positive or negative sentiment. 
get_sentiments("nrc") # associatd word with another sentiment feeling word
# View(get_sentiments("afinn"))
# View(get_sentiments("nrc"))
# we want scores not categorized words, so we will use afinn for now.
```
--> Sticking to numeric sentiment scores

Bind Sentiments
```{r bind_sentiment}
projects_score_bind <-projects_pdfwords_count %>% 
  left_join(get_sentiments("afinn"), by = "word")
# my_data4_bind <-my_data4 %>% 
#   left_join(get_sentiments("afinn"))  
View(projects_score_bind)

# Note: Many of the scores per words are NA simply because that word does not exist. 
```


```{r projectscores}
total_sentiment1 <- projects_score_bind %>% 
  filter(score !="NA") %>% 
  group_by(document) %>% 
  summarise(totals = weighted.mean(score, w = count),
            standard_dev = sd(score), 
            variance = var(score)
            )
      # note: must filter, otherwise weighted mean score will
total_sentiment <- projects_score_bind %>% 
  filter(score !="NA") %>% 
  group_by(document) %>% 
  summarise(totals = mean(score))
  
View(total_sentiment1)
View(total_sentiment)
# count_mydata3_bind <-my_data3_bind %>% 
#   count(word, score, sort = TRUE) 
# View(count_mydata3_bind)




write.csv(total_sentiment, file = "Windbelt_sen.csv")

Windbelt_sen <- read_csv("D:/Desktop/Windbelt_sen.csv")

#FOR GOOGLE
write.csv(total_sentiment, file = "Windbelt_sen_google.csv")

Windbelt_sen <- read_csv("G:/TextAnalysis/googlenews/Windbelt_sen_google.csv")

```

```{r projectscores_simple}

#total_sentiment <- split_page_text_by_word_sum_bind %>% 
 # filter(score !="NA") %>% 
  #summarise(totals = mean(score)) %>%
  #group_by()

#View(total_sentiment)

# count_mydata3_bind <-my_data3_bind %>% 
#   count(word, score, sort = TRUE) 
# View(count_mydata3_bind)

#pull into excel to create + or - column

#write.csv(windbelt_sen, file = "Windbelt_sen.csv")

#Windbelt_P_or_N <- read.csv("D:/Windbelt_sen.csv")


          


```

```{r combinewithsen}
total_sentiment_df = as.data.frame(total_sentiment)

windbelt_Full_w_sen <- merge(wind_df, total_sentiment_df, by.x ="ProjectName", by.y = "document")

windbelt_Full_w_sen <- rename(windbelt_Full_w_sen, sentiment=totals)

View(total_sentiment)
View(wind_df)
View(windbelt_Full_w_sen)
```


```{r pos_or_neg_sen}

Windbelt_P_or_N <- mutate(windbelt_Full_w_sen, p_n = ifelse(sentiment>0, "pos", "neg"))

View(Windbelt_P_or_N)

```



```{r organize_for_regressions}

#for pure sen scores

#na.omit(windbelt_Full_w_sen$Household_MeanIncome)
#na.omit(windbelt_Full_w_sen$PopDensity_mi)
#na.omit(windbelt_Full_w_sen$lr_tif)
#na.omit(windbelt_Full_w_sen$View_Score)

windbelt_Full_w_sen$H_L_W <- as.factor(windbelt_Full_w_sen$H_L_W)


windbelt_Full_w_sen$PopDensity_mi <- as.numeric(windbelt_Full_w_sen$PopDensity_mi)

windbelt_Full_w_sen$Household_MeanIncome <- as.numeric(windbelt_Full_w_sen$Household_MedianIncome)
windbelt_Full_w_sen$View_Score <- as.numeric(windbelt_Full_w_sen$View_Score)


windbelt_Full_w_sen$L_H_W <- relevel(windbelt_Full_w_sen$H_L_W, ref = "High")

str(windbelt_Full_w_sen)

summary(windbelt_Full_w_sen)


#for Neg or Pos sen scores

Windbelt_P_or_N$p_n <- as.factor(Windbelt_P_or_N$p_n)

Windbelt_P_or_N$H_L_W <- as.factor(Windbelt_P_or_N$H_L_W)


Windbelt_P_or_N$PopDensity_mi <- as.numeric(Windbelt_P_or_N$PopDensity_mi)

Windbelt_P_or_N$lr_tif <- as.factor(Windbelt_P_or_N$lr_tif)

Windbelt_P_or_N$Household_MeanIncome <- as.numeric(Windbelt_P_or_N$Household_MedianIncome)
Windbelt_P_or_N$View_Score <- as.numeric(Windbelt_P_or_N$View_Score)


Windbelt_P_or_N$L_H_W <- relevel(Windbelt_P_or_N$H_L_W, ref = "Low")

str(Windbelt_P_or_N)

summary(Windbelt_P_or_N)


```

```{r regression}

#With Pure Sen Scores

reg_TLD_VS_Sen_PopDen_MedianIncome_Cap_HL_State_Inter <- lm(TimelineDays ~ View_Score + sentiment + PopDensity_mi + Household_MedianIncome + Capacity + H_L_W + State + H_L_W*sentiment, data=windbelt_Full_w_sen)
summary(reg_TLD_VS_Sen_PopDen_MedianIncome_Cap_HL_State_Inter)

reg_TLD_VS_Sen_PopDen_MedianIncome_Cap_HL_Inter <- lm(TimelineDays ~ View_Score + sentiment + PopDensity_mi + Household_MedianIncome + Capacity + H_L_W + H_L_W*sentiment, data=windbelt_Full_w_sen)
summary(reg_TLD_VS_Sen_PopDen_MedianIncome_Cap_HL_Inter)

#reg_TL__HL_VS_SEN <- lm(TimelineDays ~ H_L_W + View_Score + sentiment + Capacity, data=windbelt_Full_w_sen)
#summary(reg_TL__HL_VS_SEN)

reg_TL_SEN <- lm(TimelineDays ~ sentiment, data=windbelt_Full_w_sen)
summary(reg_TL_SEN)

reg_TL_HL <- lm(TimelineDays ~ H_L_W, data=windbelt_Full_w_sen)
summary(reg_TL_HL)

reg_TL_VS <- lm(TimelineDays ~ View_Score, data=windbelt_Full_w_sen)
summary(reg_TL_VS)

reg_TL_POPDEN <- lm(TimelineDays ~ PopDensity_mi, data=windbelt_Full_w_sen)
summary(reg_TL_POPDEN)

reg_TL_MedianIncome <- lm(TimelineDays ~ Household_MedianIncome, data=windbelt_Full_w_sen)
summary(reg_TL_MedianIncome)

reg_SEN_VS <- lm(sentiment ~ View_Score, data=windbelt_Full_w_sen)
summary(reg_SEN_VS)

reg_SEN_HL <- lm(sentiment ~ H_L_W, data=windbelt_Full_w_sen)
summary(reg_SEN_HL)

#reg_TL__State_HL_VS_Sen_POPDEN <- lm(TimelineDays ~ State + H_L_W + View_Score + sentiment + PopDensity_mi, data=windbelt_Full_w_sen)
#summary(reg_TL__State_HL_VS_Sen_POPDEN)

#With positive/0 or negative sen
reg_PN_TL_HL_VS_POPDEN_Cap_MedianInc_State_INter <- lm(TimelineDays ~ H_L_W + View_Score + p_n + PopDensity_mi + Household_MedianIncome + Capacity + State + H_L_W*p_n, data=Windbelt_P_or_N)
summary(reg_PN_TL_HL_VS_POPDEN_Cap_MedianInc_State_INter)

reg_PN_TL__HL_VS_SEN <- lm(TimelineDays ~ H_L_W + View_Score + Pos_or_Neg, data=Windbelt_P_or_N)
summary(reg_PN_TL_HL_VS_SEN)

reg_PN_TL__SEN <- lm(TimelineDays ~ Pos_or_Neg, data=Windbelt_P_or_N)
summary(reg_PN_TL_SEN)

reg_PN_TL__HL <- lm(TimelineDays ~ H_L_W, data=Windbelt_P_or_N)
summary(reg_PN_TL_HL)

reg_PN_TL__VS <- lm(TimelineDays ~ View_Score, data=Windbelt_P_or_N)
summary(reg_PN_TL_VS)

reg_PN_TL__POPDEN <- lm(TimelineDays ~ PopDensity_mi, data=Windbelt_P_or_N)
summary(reg_PN_TL_POPDEN)

reg_PN_SEN__VS <- lm(sentiment ~ View_Score, data=Windbelt_P_or_N)
summary(reg_PN_SEN_VS)

reg_PN_SEN__HL <- lm(sentiment ~ H_L_W, data=Windbelt_P_or_N)
summary(reg_PN_SEN_HL)

reg_PN_TL__State_HL_VS_Sen_POPDEN <- lm(TimelineDays ~ State + H_L_W + View_Score + Pos_or_Neg + PopDensity_mi, data=Windbelt_P_or_N)
summary(reg_PN_TL_State_HL_VS_Sen_POPDEN)


```
```{r ttest_H_L}



```


#### Populate with negative words 
```{r negative_words}
library(stringr)
negative_words <- paste0(c('negative|postpone|against|delay|lawsuit|litigation|protest|^cost|^stop'))
# Function to replace `character(0)` with NAs as NULL values are dropped when flattening list
# inspired by: https://colinfay.me/purrr-set-na/
charnull_set <- function(x){
  p <- purrr::as_mapper(~identical(., character(0)))
  x[p(x)] <- NA
  return(x)
}
projects_pdftext_3 <- projects_pdftext %>%
  mutate(query_hits = str_extract_all(text, pattern = regex(negative_words, ignore_case=TRUE)) %>%  # Extract all the keywords
           map(~charnull_set(.x)) %>%   # Replace character(0) with NAs
           map_chr(~glue::glue_collapse(.x, sep = ";")) %>%   # collapse the multiple hits
           tolower) # all our keywords are lower case
projects_pdftext_grouped <- projects_pdftext_2 %>%
  group_by(document, query_hits)
# OR 
my_data1grouped <- my_data1 %>%
  group_by(document, query_hits)%>%
  summarise(word_list = glue::glue_collapse(query_hits, sep = ";"))
View(projects_pdftext_2)
```