---
title: "Regression_WindBelt_Regressions_plots"
author: "WINDBELT GP 2019"
date: "January 31, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



###########
# Run Regressions
########

```{r prep}

ventyx_df_NU_google_Sen <- read_csv("G:/Data/ventyx_df_NU_google_Sen.csv")

renamed_variables <- c(View_Score = "View Score",
                        Google_Sentiment = "Google News Publicity score",
                        NU_Sentiment = "Nexis Uni Publicity score",
                        PopDensity_mi = "Population Density per m2",
                        Household_MedianIncome = "Household Median Income",
                        Capacity = "Capacity",
                        H_L_WLow = "low environmental impact area"
                        # H_L_W*NU_Sentiment = "site vs. sentiment interaction"
                       )

```


###I OFFICIAL RUNS
#### NA Sentiment scores coded as '0' - w/ interaction term
##### Google only
```{r R9 OFFICIAL_RESULT}

####9. All variables included -- using only Google scores and an interaction between high-low and Google sentiment. N/A scores coded as "0"
reg_TLD_ZEROES_VS_GSen_PopDen_MedianIncome_Cap_HL_State_Inter <- lm(TimelineDays ~ View_Score + Google_Sentiment + PopDensity_mi + Household_MedianIncome + Capacity + H_L_W + State + H_L_W*Google_Sentiment, data=ventyx_df_NU_google_Sen)

names(ventyx_df_NU_google_Sen)

summary(reg_TLD_ZEROES_VS_GSen_PopDen_MedianIncome_Cap_HL_State_Inter)
summ(reg_TLD_ZEROES_VS_GSen_PopDen_MedianIncome_Cap_HL_State_Inter)
  
## note: wen env.members is present, get a google_sentiment p value=0.01029 
  ## when env.members is NOT present, get a google_sentiment p value=0.01023 
  ## coef. for google.sentiment stays same 

## everything
dwplot(reg_TLD_ZEROES_VS_GSen_PopDen_MedianIncome_Cap_HL_State_Inter, dot_args = list(colour = "firebrick"), whisker_args = list(colour = "firebrick"))+
    theme_bw()+
  ggplot2::geom_vline(xintercept = 0, colour = "black", linetype = 2)+
  labs(x = "Timeline (days)")

regression3 <- tidy(reg_TLD_ZEROES_VS_GSen_PopDen_MedianIncome_Cap_HL_State_Inter)

# Main variables
dwplot(regression3[!grepl("^State*", regression3$term),] %>%  
   relabel_predictors(renamed_variables), 
   dot_args = list(colour = "darkgreen"),
   whisker_args = list(colour = "darkgreen")
   )+
  labs(x = "Timeline (days)", y = "")+
  ggplot2::geom_vline(xintercept = 0, colour = "black", linetype = 2)+
  theme_classic()+
  # ggtitle("Regression output: all variables, using only Google scores \n and interaction term. N/A scores coded as 0:")+
  theme(legend.background = element_rect(colour="grey80"))


#Results: significance found in Google sentiment (0.01327) and capacity (0.09445)
#H_L_W: 0.63589
#Interaction: 0.204
####
#  With added text and removal of capacity/timelinedays  01/21/18
#Results: significance found in Google sentiment (0.01023) and capacity (0.06793)
#H_L_W: 0.54475
#Interaction: 0.18378
####



```

 

```{r separated_plots_variables}


library(RColorBrewer)

# View(regression1)

length(ventyx_df_google_Sen)

dwplot(regression3[!grepl("^State*|View_Score|PopDensity_mi|Household_MedianIncome|Capacity|NU_Sentiment|NU_Sentiment:H_L_WLow", regression3$term),]%>% 
 relabel_predictors(renamed_variables), 
   dot_args = list(colour = "forestgreen", lwd = 1.5),
   whisker_args = list(colour = "forestgreen", lwd = 0.8)
   )+
  labs(x = "Timeline (days)", y = "")+
  ggplot2::geom_vline(xintercept = 0, colour = "grey80", linetype = 2)+
  theme_classic()+
  # ggtitle("Regression output: all variables including NU and Google \n scores, interaction terms. N/A scores coded as 0:")+
  theme(legend.background = element_rect(colour="black"),
        axis.text.y = element_text(size = 11, hjust=1),
        axis.text.x = element_text(size = 11, hjust=1),
        axis.title.x.bottom = element_text(size=13, vjust = -1))

# View(regression3)

dwplot(regression3[!grepl("^State*|H_L_WLow|Google_Sentiment|Google_Sentiment:H_L_WLow", regression3$term),] %>% 
   relabel_predictors(renamed_variables), 
   dot_args = list(colour = "forestgreen", lwd = 1.5),
   whisker_args = list(colour = "forestgreen", lwd = 0.75)
   )+
  labs(x = "Timeline (days)", y = "")+
  ggplot2::geom_vline(xintercept = 0, colour = "grey80", linetype = 2)+
  theme_classic()+
  # ggtitle("Regression output: all variables including NU and Google \n scores, interaction terms. N/A scores coded as 0:")+
  theme(legend.background = element_rect(colour="black"),
        axis.text.y = element_text(size = 11, hjust=1),
        axis.text.x = element_text(size = 11, hjust=1),
        axis.title.x.bottom = element_text(size=13, vjust = -1))

```


#### NU only 
```{r R7}

####7. All variables included -- using only NU scores and an interaction between high-low and NU sentiment. N/A scores coded as "0".
reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter <- lm(TimelineDays ~ View_Score + NU_Sentiment + PopDensity_mi + Household_MedianIncome + Capacity + H_L_W + State + H_L_W*NU_Sentiment, data=ventyx_df_NU_google_Sen)


summ(reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter)

# 896 observations - ventyx_df_NU_google_Sen has 902 but 6 were removed as they were missing values (one more of the variables had an NA)


reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter
summary(reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter)
# dwplot(reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter)+
#   theme_bw()+
#   labs(x = "timeline")+

str(reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter)
summary(reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter)

dwplot(reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter,
       dot_args = list(colour = "firebrick"), whisker_args = list(colour = "firebrick"))+
  ggplot2::geom_vline(xintercept = 0, colour = "black", linetype = 2)+
    theme_bw()+
  labs(x = "timeline (days)")

regression2 <- tidy(reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter)

dwplot(regression2[!grepl("^State*", regression2$term),] %>%  relabel_predictors(renamed_variables),
   dot_args = list(colour = "firebrick"),
   whisker_args = list(colour = "firebrick"))+
  labs(x = "Timeline (days)", y = "")+
  ggplot2::geom_vline(xintercept = 0, colour = "black", linetype = 2)+
  theme_classic()+
  ggtitle("Regression output: all variables, using only NU scores\n and interaction term. N/A scores coded as 0:")+
  theme(legend.background = element_rect(colour="grey80"))
  
#Results: significance found in capacity (0.07323)
#NU_Sentiment: 0.505
#H_L_W: 0.643
#Interaction: 0.26455

# 01/20/18 - With added text from NU
#Results: significance found in capacity (0.05121)
#NU_Sentiment: 0.539
#H_L_W: 0.954
#Interaction: 0.56229


```

#### Google and NU 
```{r R10}
####10. All variables included -- using both NU and Google scores and an interaction between the high-low variable and both NU and Google sentiment. N/A scores coded as "0"
reg_TLD_ZEROES_VS_GNSen_PopDen_MedianIncome_Cap_HL_State_Inter <- lm(TimelineDays ~ View_Score + Google_Sentiment + NU_Sentiment + PopDensity_mi + Household_MedianIncome + Capacity + H_L_W + State + H_L_W*Google_Sentiment + H_L_W*NU_Sentiment, data=ventyx_df_NU_google_Sen)

summary(reg_TLD_ZEROES_VS_GNSen_PopDen_MedianIncome_Cap_HL_State_Inter)

dwplot(reg_TLD_ZEROES_VS_GNSen_PopDen_MedianIncome_Cap_HL_State_Inter)+
  theme_bw()+
  labs(x = "timeline")


# reg_TLD_ZEROES_VS_GNSen_PopDen_MedianIncome_Cap_HL_State$terms


# everything 
dwplot(reg_TLD_ZEROES_VS_GNSen_PopDen_MedianIncome_Cap_HL_State_Inter, dot_args = list(colour = "firebrick"), whisker_args = list(colour = "firebrick", lwd=0.5))+
  ggplot2::geom_vline(xintercept = 0, colour = "black", linetype = 2)+
    theme_classic()+
  labs(x = "timeline(days)")+
    ggtitle("Regression output: all variables, including NU and Google \n scores. N/A scores coded as 0:")+
  theme(legend.background = element_rect(colour="grey80"))


regression1 <- tidy(reg_TLD_ZEROES_VS_GNSen_PopDen_MedianIncome_Cap_HL_State_Inter)

dwplot(regression1[!grepl("^State*", regression1$term),] %>% 
   relabel_predictors(renamed_variables), 
   dot_args = list(colour = "firebrick"),
   whisker_args = list(colour = "firebrick", lwd = 0.5)
   )+
  labs(x = "Timeline (days)", y = "")+
  ggplot2::geom_vline(xintercept = 0, colour = "black", linetype = 2)+
  theme_classic()+
  ggtitle("Regression output: all variables including NU and Google \n scores, interaction terms. N/A scores coded as 0:")+
  theme(legend.background = element_rect(colour="grey80"))



#Results: significance found in Google sentiment (0.0067)
#NU_Sentiment: 0.196
#H_L_W: 0.804
#Interaction Google: 0.10846
#Interaction NU: 0.15778
####
# 01/21/18 - difference in results with changes to ventyx df and text from NU:
#Results: significance found in Google sentiment (0.00522)
#NU_Sentiment: 0.207
#H_L_W: 0.88696
#Interaction Google: 0.12861
#Interaction NU: 0.38246
####

```



### Sentiment on left hand side - NAs still coded as '0'
#### NU sentiment
```{r R11}
####11. NU Sentiment on left-hand side. N/A scores coded as "0"
reg_NSen_VS_PopDen_MedianIncome_Cap_HL_State <- lm(NU_Sentiment ~ View_Score + PopDensity_mi + Household_MedianIncome + Capacity + H_L_W + State, data=ventyx_df_NU_google_Sen)

summary(reg_NSen_VS_PopDen_MedianIncome_Cap_HL_State)

dwplot(reg_NSen_VS_PopDen_MedianIncome_Cap_HL_State)+
  theme_bw()+
  labs(x = "sentiment")

regressionA <- tidy(reg_NSen_VS_PopDen_MedianIncome_Cap_HL_State)

dwplot(regressionA[!grepl("^State*", regressionA$term),] %>% 
   relabel_predictors(renamed_variables), 
   dot_args = list(colour = "firebrick"),
   whisker_args = list(colour = "firebrick", lwd = 0.5)
   )+
  labs(x = "Sentiment score", y = "")+
  ggplot2::geom_vline(xintercept = 0, colour = "black", linetype = 2)+
  theme_classic()+
  ggtitle("Regression output: all variables including NU and Google \n scores, interaction terms. N/A scores coded as 0:")+
  theme(legend.background = element_rect(colour="grey80"))


#Results: significance found in H_L_W (0.0273)
####
# 01/21/18 - difference in results with changes to ventyx df and text from NU:
#Results: significance found in H_L_W (0.0275)


```

### Plot of interaction Term
```{r marginal_effects}
#Marginal effects of regression 14

#Covariance
vcov(reg_GSen_VS_PopDen_MedianIncome_Cap_HL_State_Memberships_Inter)
#Plot of marginal effect of interaction term. Can use mdrt.values = "minmax" to show max and min value
plot_model(reg_GSen_VS_PopDen_MedianIncome_Cap_HL_State_Memberships_Inter, type = "int", mdrt.values = "meansd") + theme_bw() + xlab("Habitat Impact") + ylab("Timeline (days)\n") + ggtitle("Marginal Effect of Interaction Term")
#Can use the scale function to "mean-center" the data
#Is the sum of alpha 1 (google sentiment) and alpha 3 (interaction term) different than zero
#restricted vs unrestricted model. 

```


##II OTHER RUNS
### Sentiment on the left hand side:

#### Google sentiment
```{r R12}
####12. Google Sentiment on left-hand side. N/A scores coded as "0"
reg_GSen_VS_PopDen_MedianIncome_Cap_HL_State <- lm(Google_Sentiment ~ View_Score + PopDensity_mi + Household_MedianIncome + Capacity + H_L_W + State, data=ventyx_df_NU_google_Sen)

summary(reg_GSen_VS_PopDen_MedianIncome_Cap_HL_State)

# dwplot(reg_GSen_VS_PopDen_MedianIncome_Cap_HL_State)+
#   theme_bw()+
#   labs(x = "timeline")
# 

regressionB <- tidy(reg_GSen_VS_PopDen_MedianIncome_Cap_HL_State)

dwplot(regressionB[!grepl("^State*", regressionB$term),] %>% 
   relabel_predictors(renamed_variables), 
   dot_args = list(colour = "firebrick"),
   whisker_args = list(colour = "firebrick", lwd = 0.5)
   )+
  labs(x = "Sentiment score", y = "")+
  ggplot2::geom_vline(xintercept = 0, colour = "black", linetype = 2)+
  theme_classic()+
  ggtitle("Regression output: all variables including NU and Google \n scores, interaction terms. N/A scores coded as 0:")+
  theme(legend.background = element_rect(colour="grey80"))



#Results no significance found
#H_L_W: 0.154
####
# 01/21/18 - difference in results with changes to ventyx df and text from NU:
#H_L_W: 0.16372
#capacity: 0.11

```



# All variables included -- using only NU scores and an interaction between high-low and NU sentiment. N/A scores coded as "0".
```{r R7}

####7. All variables included -- using only NU scores and an interaction between high-low and NU sentiment. N/A scores coded as "0".
reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter <- lm(TimelineDays ~ View_Score + NU_Sentiment + PopDensity_mi + Household_MedianIncome + Capacity + H_L_W + State + H_L_W*NU_Sentiment, data=ventyx_df_NU_google_Sen)


summ(reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter)

# 896 observations - ventyx_df_NU_google_Sen has 902 but 6 were removed as they were missing values (one more of the variables had an NA)


reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter
summary(reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter)
# dwplot(reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter)+
#   theme_bw()+
#   labs(x = "timeline")+

str(reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter)
summary(reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter)

dwplot(reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter,
       dot_args = list(colour = "firebrick"), whisker_args = list(colour = "firebrick"))+
  ggplot2::geom_vline(xintercept = 0, colour = "black", linetype = 2)+
    theme_bw()+
  labs(x = "timeline (days)")

regression2 <- tidy(reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter)

dwplot(regression2[!grepl("^State*", regression2$term),] %>%  relabel_predictors(renamed_variables),
   dot_args = list(colour = "firebrick"),
   whisker_args = list(colour = "firebrick"))+
  labs(x = "Timeline (days)", y = "")+
  ggplot2::geom_vline(xintercept = 0, colour = "black", linetype = 2)+
  theme_classic()+
  ggtitle("Regression output: all variables, using only NU scores\n and interaction term. N/A scores coded as 0:")+
  theme(legend.background = element_rect(colour="grey80"))
  
#Results: significance found in capacity (0.07323)
#NU_Sentiment: 0.505
#H_L_W: 0.643
#Interaction: 0.26455

# 01/20/18 - With added text from NU
#Results: significance found in capacity (0.05121)
#NU_Sentiment: 0.539
#H_L_W: 0.954
#Interaction: 0.56229



```



```{r combined_with_interaction term}


R1 <- reg_TLD_ZEROES_VS_GNSen_PopDen_MedianIncome_Cap_HL_State_Inter
R2 <- reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter
R3 <- reg_TLD_ZEROES_VS_GSen_PopDen_MedianIncome_Cap_HL_State_Inter

# general_everything plot

# unique(regression1$term)

# dwplot(list(tidy(R1),tidy(R2),tidy(R3), conf.int = FALSE)
#        # dot_args = list(colour = "firebrick"), whisker_args = list(colour = "firebrick")
#        )+
#     theme_bw()+
#   labs(x = "timeline")


### does not work unless subset by regression 
regression1_1 <- tidy(R1)  %>% 
  filter(!grepl('^State*', term)) %>% 
  mutate(model = "regression1_G+NU")

regression2_1 <- tidy(R2)  %>% 
  filter(!grepl('^State*', term)) %>% 
  mutate(model = "regression2_NU")

regression3_1 <- tidy(R3)  %>% 
  filter(!grepl('^State*', term)) %>% 
  mutate(model = "regression3_G")

combined_reg <-  bind_rows(regression1_1, regression2_1, regression3_1)
# View(combined_reg)


dwplot(combined_reg %>% 
   relabel_predictors(renamed_variables), 
   dot_args = list(aes(shape = model)),
   whisker_args = list(aes(colour = model))
   )+
  labs(x = "Timeline (days)", y = "")+
  ggplot2::geom_vline(xintercept = 0, colour = "grey80", linetype = 2)+
  theme_classic()+
  ggtitle("Combined regression outputs with interaction term:\n N/A scores coded as 0:\n")+
  theme(plot.title = element_text(face="bold"),
          legend.position = c(0.7, 0.77),
          legend.justification = c(0, 0),
          legend.background = element_rect(colour = "grey60"),
          legend.title.align = .5)
  



```

#### NU sentiment=environmental membership added + interact term
```{r R13}
####13. Timeline on left-hand side, using NU sentiment. Interaction term between NU and high-low impact. Environmental memberships variable added. N/A scores coded as 0
reg_NSen_VS_PopDen_MedianIncome_Cap_HL_State_Memberships_Inter <- lm(TimelineDays ~ View_Score + NU_Sentiment + members_env + PopDensity_mi + Household_MedianIncome + Capacity + H_L_W + State + H_L_W*NU_Sentiment, data=ventyx_df_NU_google_Sen)

summary(reg_NSen_VS_PopDen_MedianIncome_Cap_HL_State_Memberships_Inter)
dwplot(tidy(reg_NSen_VS_PopDen_MedianIncome_Cap_HL_State_Memberships_Inter))
```

#### Google sentiment=environmental membership added + interact term
```{r R14}
####14. Timeline on left-hand side, using Google sentiment. Interaction term between Google and high-low impact. Environmental memberships variable added. N/A scores coded as 0
reg_GSen_VS_PopDen_MedianIncome_Cap_HL_State_Memberships_Inter <- lm(TimelineDays ~ View_Score + Google_Sentiment + members_env + PopDensity_mi + Household_MedianIncome + Capacity + H_L_W + State + H_L_W*Google_Sentiment, data=ventyx_df_NU_google_Sen)

summary(tidy(reg_GSen_VS_PopDen_MedianIncome_Cap_HL_State_Memberships_Inter))

dwplot(tidy(reg_GSen_VS_PopDen_MedianIncome_Cap_HL_State_Memberships_Inter))
```


### NA Sentiment scores coded as '0' - No interaction term

#### NU and Google 
```{r R5}

####5. All variables included -- using both NU and Google scores. N/A scores coded as "0":

reg_TLD_ZEROES_VS_GNSen_PopDen_MedianIncome_Cap_HL_State <- lm(TimelineDays ~ View_Score + Google_Sentiment + NU_Sentiment + PopDensity_mi + Household_MedianIncome + Capacity + H_L_W + State, data=ventyx_df_NU_google_Sen)

summary(reg_TLD_ZEROES_VS_GNSen_PopDen_MedianIncome_Cap_HL_State)

# reg_TLD_ZEROES_VS_GNSen_PopDen_MedianIncome_Cap_HL_State$terms

renamed_variables <- c(View_Score = "View Score",
                        Google_Sentiment = "Google News Publicity score",
                        NU_Sentiment = "Nexis Uni Publicity score",
                        PopDensity_mi = "Population Density per m2",
                        Household_MedianIncome = "Household Median Income",
                        Capacity = "Capacity",
                        H_L_WLow = "High vs. low impact area")

# everything 
dwplot(tidy(reg_TLD_ZEROES_VS_GNSen_PopDen_MedianIncome_Cap_HL_State), dot_args = list(colour = "firebrick"), whisker_args = list(colour = "firebrick", lwd=0.5))+
  ggplot2::geom_vline(xintercept = 0, colour = "black", linetype = 2)+
    theme_classic()+
  labs(x = "timeline")+
    ggtitle("Regression output: all variables, including NU and Google scores. N/A \n scores coded as 0:")+
  theme(legend.background = element_rect(colour="grey80"))


regression1 <- tidy(reg_TLD_ZEROES_VS_GNSen_PopDen_MedianIncome_Cap_HL_State)

dwplot(regression1[!grepl("^State*", regression1$term),] %>% 
   relabel_predictors(renamed_variables), 
   dot_args = list(colour = "firebrick"),
   whisker_args = list(colour = "firebrick", lwd = 0.5)
   )+
  labs(x = "Timeline (days)", y = "")+
  ggplot2::geom_vline(xintercept = 0, colour = "black", linetype = 2)+
  theme_classic()+
  ggtitle("Regression output: all variables, including NU and Google scores. N/A \n scores coded as 0:")+
  theme(legend.background = element_rect(colour="grey80"))
  

#Results: significance found in Google sentiment (0.02867) and capacity (0.09094)
#H_L_W p-value: 0.91039
#NU_Sentiment: 0.57313
####
## 01/20/18 - MS: with additional text, got more significance on some values it seems 

```

#### NU only
```{r R6}
####6. All variables included -- using only NU scores. N/A scores coded as "0".
reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State <- lm(TimelineDays ~ View_Score + NU_Sentiment + PopDensity_mi + Household_MedianIncome + Capacity + H_L_W + State, data=ventyx_df_NU_google_Sen)

summary(reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State)

dwplot(reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State, dot_args = list(colour = "firebrick"), whisker_args = list(colour = "firebrick"))+
  ggplot2::geom_vline(xintercept = 0, colour = "black", linetype = 2)+
    theme_bw()+
  labs(x = "timeline")

regression2 <- tidy(reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State)

dwplot(regression2[!grepl("^State*", regression2$term),] %>% 
   relabel_predictors(renamed_variables), 
   dot_args = list(colour = "firebrick"),
   whisker_args = list(colour = "firebrick")
   )+
  labs(x = "Timeline (days)", y = "")+
  ggplot2::geom_vline(xintercept = 0, colour = "black", linetype = 2)+
  theme_classic()+
  ggtitle("Regression output: all variables, using only NU scores. N/A \n scores coded as 0:")+
  theme(legend.background = element_rect(colour="grey80"))
  

#Results: significance found in capacity (0.07004)
#NU_Sentiment: 0.986
#H_L_W: 0.856

```

```{r R7}
####7. All variables included -- using only NU scores and an interaction between high-low and NU sentiment. N/A scores coded as "0".
reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State_Inter <- lm(TimelineDays ~ View_Score + NU_Sentiment + PopDensity_mi + Household_MedianIncome + Capacity + H_L_W + State + H_L_W*NU_Sentiment, data=ventyx_df_NU_google_Sen)

## 01/20/18 - MS: with additional text, got more significance on values 
#Results: significance found in capacity (0.04916)
#NU_Sentiment: 0.73846
#H_L_W: 0.73898

```

#### Google only
```{r R8}

####8. All variables included -- using only Google scores. N/A scores coded as "0"
reg_TLD_ZEROES_VS_GSen_PopDen_MedianIncome_Cap_HL_State <- lm(TimelineDays ~ View_Score + Google_Sentiment + PopDensity_mi + Household_MedianIncome + Capacity + H_L_W + State, data=ventyx_df_NU_google_Sen)

summary(reg_TLD_ZEROES_VS_GSen_PopDen_MedianIncome_Cap_HL_State)

## everything
dwplot(tidy(reg_TLD_ZEROES_VS_GSen_PopDen_MedianIncome_Cap_HL_State), dot_args = list(colour = "firebrick"), whisker_args = list(colour = "firebrick"))+
    theme_bw()+
  ggplot2::geom_vline(xintercept = 0, colour = "black", linetype = 2)+
  labs(x = "Timeline (days)")

regression3 <- tidy(reg_TLD_ZEROES_VS_GSen_PopDen_MedianIncome_Cap_HL_State) %>% 
  mutate()

# Main variables
dwplot(regression3[!grepl("^State*", regression3$term),] %>%  
   relabel_predictors(renamed_variables), 
   dot_args = list(colour = "firebrick"),
   whisker_args = list(colour = "firebrick")
   )+
  labs(x = "Timeline (days)", y = "")+
  ggplot2::geom_vline(xintercept = 0, colour = "black", linetype = 2)+
  theme_classic()+
  ggtitle("Regression output: all variables, using only Google scores. N/A \n scores coded as 0:")+
  theme(legend.background = element_rect(colour="grey80"))


#Results: significance found in Google sentiment (0.02972) and capacity (0.08989)
#H_L_W: 0.93917
#
####
## 01/20/18 - MS: with additional text, got more significance on values 
# Results: significance found in Google sentiment (0.02486) and capacity (0.06455)
# H_L_W: 0.84519


```


```{r COmparative dotwhiskerplot}

R1 <- reg_TLD_ZEROES_VS_GNSen_PopDen_MedianIncome_Cap_HL_State
R2 <- reg_TLD_ZEROES_VS_NSen_PopDen_MedianIncome_Cap_HL_State
R3 <- reg_TLD_ZEROES_VS_GSen_PopDen_MedianIncome_Cap_HL_State

# general_everything plot

# unique(regression1$term)
# 
# dwplot(list(tidy(R1),tidy(R2),tidy(R3), conf.int = FALSE)
#        # dot_args = list(colour = "firebrick"), whisker_args = list(colour = "firebrick")
#        )+
#     theme_bw()+
#   labs(x = "timeline")



### does not work unless subset by regression 
regression1_1 <- tidy(R1)  %>% 
  filter(!grepl('^State*', term)) %>% 
  mutate(model = "regression1_G+NU")

regression2_1 <- tidy(R2)  %>% 
  filter(!grepl('^State*', term)) %>% 
  mutate(model = "regression2_NU")

regression3_1 <- tidy(R3)  %>% 
  filter(!grepl('^State*', term)) %>% 
  mutate(model = "regression3_G")

combined_reg <-  bind_rows(regression1_1, regression2_1, regression3_1)
View(combined_reg)


dwplot(combined_reg %>% 
   relabel_predictors(renamed_variables), 
   dot_args = list(aes(shape = model)),
   whisker_args = list(aes(colour = model))
   )+
  labs(x = "Timeline (days)", y = "")+
  ggplot2::geom_vline(xintercept = 0, colour = "grey80", linetype = 2)+
  theme_classic()+
  ggtitle("Combined regression outputs;\n N/A scores coded as 0:")+
  theme(plot.title = element_text(face="bold"),
          legend.position = c(0.65, 0.8),
          legend.justification = c(0, 0),
          legend.background = element_rect(colour = "grey60"),
          legend.title.align = .5)
  
# install.packages("jtools")
# library(jtools)
# plot_summs(tidy(R1), scale = TRUE, plot.distributions = TRUE, inner_ci_level = .9)
#  coefplot()

```



```{r R14}
####14. Timeline on left-hand side, using Google sentiment. Interaction term between Google and high-low impact. Environmental memberships variable added. N/A scores coded as 0
reg_GSen_VS_PopDen_MedianIncome_Cap_HL_State_Memberships_Inter <- lm(TimelineDays ~ View_Score + Google_Sentiment + members_env + PopDensity_mi + Household_MedianIncome + Capacity + H_L_W + State + Google_Sentiment*H_L_W, data=ventyx_df_NU_google_Sen)

summary(reg_GSen_VS_PopDen_MedianIncome_Cap_HL_State_Memberships_Inter)
dwplot(tidy(reg_GSen_VS_PopDen_MedianIncome_Cap_HL_State_Memberships_Inter))
```


