---
title: "NexisUni_pdf_scraping"
author: "Margaux Sleckman"
date: "October 18, 2018"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

#### Outline of lexisUni text analysis (checked if done):
 1. Dowload pdf from lexisUni - search terms: "Master Project Name" AND "Project Developer" AND "wind" AND "energy' (if necessary, the state was added in the search term if location was not precise enough. 
 2. Save pdf in sample_pdfs folder x
      Each pdf saved as "fulltext"+ # search results if <10" + "abbreved project developer" "# of results pages in         >10", collapsed with "_" x
2. Create a df with everypdf in each row. my_data x
3. Create df with unested text unested,such that each row is a pdf page.x
4. Created new df that splits each page by word, sch that every row is a word in the text (unest_tokens where tokens are pdf) x
5. Get word count of specific words through group_by()
Conduct sentiment analysis on unique words x 
6. get hits and number of hits of different 'negative words' x

# Following meeting 10/22/18:
1. Unest token by group of words or sentences and conduct sentiment analysis on this.
2. Clean scripts - ID words in pdf that consistently pop up and need to be filtered out.
3. separate headlines from text to ensure we don't have duplicates
4. create csv format (NAME, Developer, State, Sentiment, subjectivity ...)

Other notes: 
*tidytext::tokenize function - every element in list become df. rbind dfs 
 str_count() how many times does a search term come up 
 str_match()
 regex() 

```{r packages_read_in}

### Packages 

# install.packages("pdftools", "devtools")
library(pdftools)
library(tm)
# library(tm.plugin.lexisnexis)
library(devtools)
# install.packages("tidytext")
library(tidytext)
library(broom)
# install.packages("tidyverse")
library(data.table)
library(tidyverse)
library(purrr)

library(googledrive)

```


```{r setup}

drive_auth()
# googledrive::drive_auth()
team_drive <- team_drive_get("Bren GP 2019 WindBelt/WindBelt GP")
GPteam_drive_id <- team_drive$id
NexisUni <- drive_ls(GPteam_drive_id, path = "~/")
drive_folder <- ""
googledrive::drive_get(path = )


directory <- "G:/TextAnalysis/NexisUni/Margaux_PDFs"

# directory <- "G:/TextAnalysis/NexisUni/"
"D:/ "

#change path if not on windbelt comp.
pdfs <- paste(directory, "/", list.files(directory, pattern = "*.pdf", ignore.case = T), sep = "")
pdfs_names <- list.files(directory, pattern = "*.pdf", ignore.case = T)
# pdfs_names
pdfs_text <- purrr::map(pdfs, pdftools::pdf_text)
# head(pdfs_text,2)

```

#### Dataframe 1 with just pdfs and full text of the pdf
```{r dataframe1}

#each row is a pdf doc name (document) with the full pdf text

projects_pdftext <- data_frame(document = pdfs_names, text = pdfs_text)
head(projects_pdftext)
View(projects_pdftext)

# text column : each row is an element of a list 

```

#### Dataframe 2 spliting text by page
```{r dataframe2}

# dataset with each page in one row
project_pdfpages <- projects_pdftext %>% 
  unnest() # splits pdf text by page and removes list format ( c("")) since each element of the list is now its own row.

View(project_pdfpages)

```

#### Dataframe 3 spliting page text by word (unnest_tokens())
```{r dataframe3}

#Dataset with each work in or row associated with its pdf source 
projects_pdfwords <- projects_pdftext %>% 
  unnest() %>% 
  tidytext::unnest_tokens(output = word, input = text, token = 
                          "words", to_lower = T
                # strip_numeric = TRUE
                )%>%      
  filter(!word %in% c("lexis",
                      "nexis", "Uni",
                      "about lexisnexis",
                      "Privacy Policy",
                      "Terms & Conditions", "Copyright © 2018 LexisNexis",
                      " | ",  "@", "lexisnexis")) 

# %>% gsub("[^A-Za-z0-9,;._-]","")
View(projects_pdfwords)

projects_pdfnest <- projects_pdftext %>% 
  unnest() %>% 
  tidytext::unnest_tokens(output = ngrams, input = text, token = "ngrams", n = 5, to_lower = T)

# View(my_data4)

# note: unnest_tokens() splits text by respective element (ie word, phrase, ...) word is default

```

#### Dataframe wordsgrouped by pdf and summarised by frequency of word or ngrams
```{r group_by}

projects_pdfwords_count <- projects_pdfwords %>%
  group_by(document, word) %>% 
  summarise(count = n())

# View(projects_pdfwords_count)

# counts the number of time a specific words is found in the page pdf.
# View(my_data2_sum)

projects_pdfnest_count <- projects_pdfnest %>%
  group_by(document, ngrams) %>% 
  summarise(count = n())

# View(projects_pdfnest_count)
# add new count column with most freq. words
```

#### Sentiment dictionaries:

Compare sentiment dictionaries
```{r sentimentdictionaries}

# using 'afinn' vs. 'nrc sentiment tests.
get_sentiments("afinn") # associates word with a sentiment score
#afinn scores/ranks from -5 to +5 for positive or negative sentiment. 

get_sentiments("nrc") # associatd word with another sentiment feeling word

# View(get_sentiments("afinn"))

# View(get_sentiments("nrc"))

# we want scores not categorized words, so we will use afinn for now.

```
--> Sticking to numeric sentiment scores

Bind Sentiments
```{r bind_sentiment}

projects_score_bind <-projects_pdfwords_count %>% 
  left_join(get_sentiments("afinn"), by = "word")

# my_data4_bind <-my_data4 %>% 
#   left_join(get_sentiments("afinn"))  

View(projects_score_bind)
# Note: Many of the scores per words are NA simply because that word does not exist. 

```


```{r projectscores}


total_sentiment1 <- projects_score_bind %>% 
  filter(score !="NA") %>% 
  group_by(document) %>% 
  summarise(totals = weighted.mean(score, w = count),
            standard_dev = sd(score), 
            variance = var(score)
            )

      # note: must filter, otherwise weighted mean score will
total_sentiment <- projects_score_bind %>% 
  filter(score !="NA") %>% 
  group_by(document) %>% 
  summarise(totals = mean(score))
  
View(total_sentiment1)
View(total_sentiment)

# count_mydata3_bind <-my_data3_bind %>% 
#   count(word, score, sort = TRUE) 
# View(count_mydata3_bind)

```

#### Populate with negative words 
```{r negative_words}

library(stringr)

negative_words <- paste0(c('negative|postpone|against|delay|lawsuit|litigation|protest|^cost|^stop'))

# Function to replace `character(0)` with NAs as NULL values are dropped when flattening list
# inspired by: https://colinfay.me/purrr-set-na/

charnull_set <- function(x){
  p <- purrr::as_mapper(~identical(., character(0)))
  x[p(x)] <- NA
  return(x)
}

projects_pdftext_3 <- projects_pdftext %>%
  mutate(query_hits = str_extract_all(text, pattern = regex(negative_words, ignore_case=TRUE)) %>%  # Extract all the keywords
           map(~charnull_set(.x)) %>%   # Replace character(0) with NAs
           map_chr(~glue::glue_collapse(.x, sep = ";")) %>%   # collapse the multiple hits
           tolower) # all our keywords are lower case

projects_pdftext_grouped <- projects_pdftext_2 %>%
  group_by(document, query_hits)
# OR 
my_data1grouped <- my_data1 %>%
  group_by(document, query_hits)%>%
  summarise(word_list = glue::glue_collapse(query_hits, sep = ";"))

View(projects_pdftext_2)

```

